---
title: "P8105 HW6"
author: JingYao Geng
date: '`r format(Sys.time(), "%Y-%m-%d")`'
output: github_document
---

```{r setup, include = FALSE}
library(tidyverse)
library(viridis)
library(modelr)
library(mgcv)


knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%", 
  fig.align = 'center',
  message = FALSE,
  warning = FALSE,
  collapse = TRUE,
  echo = TRUE
)

theme_set(theme_minimal() + 
          theme(legend.position = "bottom") +
          theme(plot.title = element_text(hjust = 0.5, size = 15, face = "bold")) +
          theme(plot.subtitle = element_text(hjust = 0.5))
          )

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Problem 1

```{r}
homicide_df = 
  read_csv("data-homicides-master/homicide-data.csv", na = c("", "NA", "Unknown")) %>% 
  mutate(
    city_state = str_c(city, state, sep = ", "),
    victim_age = as.numeric(victim_age),
    resolution = case_when(
      disposition == "Closed without arrest" ~ 0,
      disposition == "Open/No arrest"        ~ 0,
      disposition == "Closed by arrest"      ~ 1)
  ) %>% 
  filter(
    victim_race %in% c("White", "Black"),
    city_state != "Tulsa, AL") %>% 
  select(city_state, resolution, victim_age, victim_race, victim_sex)
```


Start with one city.

```{r}
baltimore_df =
  homicide_df %>% 
  filter(city_state == "Baltimore, MD")
glm(resolution ~ victim_age + victim_race + victim_sex, 
    data = baltimore_df,
    family = binomial()) %>% 
  broom::tidy() %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(term, OR, starts_with("CI")) %>% 
  knitr::kable(digits = 3)
```


Try this across cities.

```{r}
models_results_df = 
  homicide_df %>% 
  nest(data = -city_state) %>% 
  mutate(
    models = 
      map(.x = data, ~glm(resolution ~ victim_age + victim_race + victim_sex, data = .x, family = binomial())),
    results = map(models, broom::tidy)
  ) %>% 
  select(city_state, results) %>% 
  unnest(results) %>% 
  mutate(
    OR = exp(estimate),
    CI_lower = exp(estimate - 1.96 * std.error),
    CI_upper = exp(estimate + 1.96 * std.error)
  ) %>% 
  select(city_state, term, OR, starts_with("CI")) 
```

```{r}
models_results_df %>% 
  filter(term == "victim_sexMale") %>% 
  mutate(city_state = fct_reorder(city_state, OR)) %>% 
  ggplot(aes(x = city_state, y = OR)) + 
  geom_point() + 
  geom_errorbar(aes(ymin = CI_lower, ymax = CI_upper)) + 
  theme(axis.text.x = element_text(angle = 90, hjust = 1))
```


## Problem 2

**1. Data Import**
```{r import2}
# Import
birthweight = read_csv("./data#2/birthweight.csv") %>%
  janitor::clean_names()

# str(birthweight)

# Tidy
birthweight = 
  birthweight %>%
  mutate(
    babysex = factor(babysex, levels = c(1,2), labels = c("male", "female")),
    frace = factor(frace, levels = c(1, 2, 3, 4, 8, 9), labels = c("white", "black", "asian"," puerto rican", "other", "unknown")),
    malform = factor(malform, labels = c("absent", "present")),
    mrace = factor(mrace,  c(1, 2, 3, 4, 8, 9), labels = c("white", "black", "asian"," puerto rican", "other", "unknown")),
    
    # pounds to grams
    delwt = delwt * 453.59237,
    ppwt = ppwt * 453.59237,
    wtgain = wtgain * 453.59237,
   
    mrace = fct_infreq(mrace),
    babysex = fct_infreq(babysex)
    )

# ways to check the existence of missing values:
#sum(is.na(birthweight))
#sum(!complete.cases(birthweight))

```

There are `r nrow(read_csv("./data#2/birthweight.csv"))` observations  and `r ncol(read_csv("./data#2/birthweight.csv"))`variables in the `birthweight` dataset. And there is `r sum(is.na(birthweight))` missing value in the dataset. In order to do the following analyses, we convert the numeric variables `babysex`, `frace`, `malform`, and `mrace` into factor variables, and also adjust the unit from `pounds` to `grams` for variable `delwt`, `ppwt` and `wtgain`. 

**Overview: regression model based on all available variables**
```{r all_var}
all = lm(bwt~.,data = birthweight)
summary(all)
```
Based on the summary table of regression on all the variables, I decide to select variables with a p value of coefficient that is smaller than 0 into my model.

**My model:**

* Response: bwt: baby’s birth weight (grams)
* Predictors: 
  * babysex: baby's sex
  * bhead: baby's head circumference at birth (cm)
  * blength: baby's length at birth (cm)
  * delwt: month's weight at delivery (pounds)
    * need to convert to grams!
  * gaweeks: gestational age in weeks
  * mrace: mother's race
  * parity: number of live births prior to this pregnancy.
  * smoken: average number of cigarettes smoked per day during pregnancy
  
```{r my_model}
my_model = lm(bwt ~ babysex + bhead + blength + delwt + smoken, data = birthweight) 
my_model %>% broom::tidy() %>% knitr::kable()
# summary(my_model)
```

**My_model: A plot of model residuals against fitted values**
```{r resid_fit_plot}
pred_vs_resid =  
    birthweight %>% 
    add_predictions(my_model) %>% 
    add_residuals(my_model) %>% 
    select(pred, resid) %>%
    ggplot(aes(x = pred, y = resid)) + 
    geom_point(alpha = 0.5, size = 0.8, color = "lightblue")  + 
    geom_smooth(method = "lm", color = "red", linetype = 2) + 
    #geom_line(aes(y = 0), linetype = "dashed", color = "red") +
    #geom_hline(yintercept = 0, color = "red", size = 1, linetype = 2) +
    labs(title = "Predicted vs Residuals", 
       x = "Predicted (grams)", 
       y = "Residuals (grams)")
```


**Compare my model to the following two models:**
```{r model_compare}
# One using length at birth and gestational age as predictors (main effects only)
model1 = lm(bwt ~ blength + gaweeks, data = birthweight) %>%
  #broom::glance() %>% 
  broom::tidy() %>%
  knitr::kable()
#One using head circumference, length, sex, and all interactions (including the three-way interaction) between these
model2 = lm(bwt ~ bhead * blength * babysex, data = birthweight) %>%
  #broom::glance() %>%
  broom::tidy() %>%
  knitr::kable()

model1; model2
```


**Cross validation comparisons:**
```{r cross_v}
# test/train datasets
cv_bw = 
    crossv_mc(birthweight, 200) %>% 
    mutate(
        train = map(train, as.tibble),
        test = map(test,as.tibble)
    ) 
# rmse values for iterated linear models
cv_bw = cv_bw %>% 
    mutate(
        my_model = map(train,~lm(bwt ~ babysex + bhead + blength + delwt + mrace + gaweeks + smoken, data = .x)),
        model1 = map(train,~lm(bwt ~ blength + gaweeks, data = .x)),
        model2 = map(train,~lm(bwt ~ bhead * blength * babysex, data = .x))
    ) %>% 
    mutate(
        rmse_my_model = map2_dbl(my_model, test, ~rmse(model = .x,data = .y)),
        rmse_model1 = map2_dbl(model1, test, ~rmse(model = .x,data = .y)),
        rmse_model2 = map2_dbl(model2, test, ~rmse(model = .x,data = .y))
    )

# plot of comparisons
cv_bw %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "models",
    values_to = "rmse",
    names_prefix = "rmse_"
  ) %>% 
  mutate(
    models = fct_reorder(models,rmse)) %>% 
  ggplot(aes(x = models, y = rmse)) +
  geom_violin() +
  labs(
        title = "Cross Validation Comparisons",
        x = "Model",
        y = "Root Mean Squared Error")
    
```

## Problem 3

**1. Data Import**
```{r import3}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```


